Supplementary Information

### 2020-08-17 doc/manuscript/MEE_manuscript.Rmd
update manuscript

Second, we combined candidate climate drivers and reconstructed $DBH$ data in a GLS model (Fig. 1). 
*(DBH not included in models focused on climate sensitivity.)*
We checked for collinearity among the full set of variables using the *vifstep* function (**REF**) and removed any variable with a variance inflation factor > 3. 
For each species (at each site) independently, we ran a GLS model including every combination of the candidate climate variables (as a 2-degree polynomial to allow quadratic curve), $DBH$, and fit one year spline for each treeID, plus a random intercept for each tree. 
Wealso ran models with a spline of DBH (3 knots).
Across all possible models, variable AICc weights were summed to determine which drivers are most important. 
We considered the model containing those variables as the top model.

>>>>

Second, we combined candidate climate drivers and reconstructed $DBH$ data in a GLS model (Fig. 1). 
*(DBH not included in models focused on climate sensitivity.)*
We checked for collinearity among the full set of variables using the *vifstep* function (**REF**) and removed any variable with a variance inflation factor > 3. 
For each species (at each site) independently, we ran a GLS model including every combination of the candidate climate variables (as a 2-degree polynomial to allow quadratic curve), $DBH$, and fit one year spline for each treeID, plus a random intercept for each tree. 
We also ran models with a spline of DBH (3 knots).
Across all possible models, variable AICc weights were summed to determine which drivers are most important. (*Valentine, we'll need some more details here.*)
We considered the model containing those variables as the top model, noting that the top model can contain terms that are not individually significant in the context of that model.
